A Review of\\ IDSGAN: Generative Adversarial Networks for Attack Generation against Intrusion Detection

### 2019-10-16 MTech/CS607/Paper Review/Paper_Review.tex
Paper Review: Added Paper Review for 1809.02077

\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.035} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics

@@

\usepackage[hmarginratio=1:1,top=18mm,bottom=18mm,left=12mm,
right=12mm,columnsep=15pt]{geometry} % Document margins

@@

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
\posttitle{\end{center}} % Article title closing formatting
\title{A Review of\\ Adversarial Machine Learning\\ 
\huge{(4th ACM Workshop on AISec, Oct. 2011,43-58)}} % Article title
\author{%
\Large \textsc{Rohit Das}\\ % Your name
\large ID No.: 11910230\\
\large M. Tech. (CSE)\\
Reviewers: Dr. Sk Subidh Ali, and Dr. Subhajit Sidhanta
}
\date{\today} % Leave empty to omit a date

@@

\lettrine[nindent=0em,lines=3]{T} he manuscript by Huang et. al. focuses primarily on the security fault lines in modern Machine Learning, how they can be utilized to break into secure learning systems, and manipulate data and users. It also sequentially outlines how such situations can be avoided by keeping some points in mind while designing a new or improving an existing learning algorithm or model, forming the crux of Adversarial Machine Learning.

@@

Listed below are the milestones covered by the paper: 
\begin{itemize}
\item A good overview of Adversarial Machine Learning and its impact in the field of modern Artificial Intelligence.

\item Taxonomy of influence, security violations and specificity of attack by a potential adversary on a learning system.

\item Modeling secure learning systems as a game between an attacker and a defender, and how both can influence the learning algorithm, learning and evaluation of data, as well as the data itself. It also subtly creates the idea that a learning model can be made more robust by artificially creating an adversary and training the model with it.

\item An elaborate section on Causative attacks to learning systems, well-documented with graphs and data. It also contains case studies on two algorithms: SpamBayes and Principal Component Analysis (PCA)-based anomalous network traffic detector. The authors have highlighted the strengths of an attacker given certain degrees of freedom, and how they can be countered.

\item A section on Exploratory attacks, discussing various evasion techniques, theoretical and practical, and how the most optimum evasion techniques are not the ones generally implemented in real time.

\item Privacy violations, and advantages and roles of randomization of functions and parameters in learning models.
\end{itemize}

@@

\section{Best Elements}
Below mentioned are the best elements of the paper:
\begin{itemize}
\item All conclusions, facts and experiments have been well-supported with relevant data and graphs. The graphs clearly highlight the differences between using a robust and a non-secure learning model.

\item The paper mainly focuses on causative attacks, the most malicious of attacks, and extensive research has been done into its types, variants and countermeasures.

\item The two algorithms used as case studies are very much used in real life situations, and hence makes the paper very relevant in today's new age of Artificial Intelligence, thereby easily underlining the need for the topic researched on.

\item Privacy, being a trending concept throughout history and a fundamental human right, is also a part of this paper, and makes it a must-read for researchers in this field.
\end{itemize}
%------------------------------------------------
%
\section{Limitations}
\begin{itemize}
\item A section on image and pattern recognition, and how adversaries can trick such models, could have been made a part of the research, as it is a budding novel area in Machine Learning, and specifically, Deep Learning.
\item The paper is a bit too textual. Adding more images would have helped better illustrate the various attacks and countermeasures presented here.
\end{itemize}
%
%-----------------------------------------------------------------------
%
\section{Opinion}
~~~~~The paper gives a good introduction and an elaborate explanation on Adversarial Machine Learning, and how to counter it. It aptly highlights the necessity and relevance of securing learning models, especially when they will be planned to be used in mission-critical situations. However, the organization of the paper could be improved by including more references in the analyses.
%
%-----------------------------------------------------------------------

>>>>

\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{0.96} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics

@@

\usepackage[hmarginratio=1:1,top=15.5mm,bottom=18mm,left=12mm,
right=12mm,columnsep=14pt]{geometry} % Document margins

@@

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
\posttitle{\end{center}} % Article title closing formatting
\title{A Review of\\ IDSGAN: Generative Adversarial Networks for Attack Generation against Intrusion Detection} % Article title
\author{%
\Large \textsc{Rohit Das}\\ % Your name
\large ID No.: 11910230\\
\large M. Tech. (CSE)\\
Reviewer: Dr. Sk Subidh Ali}
\date{\today} % Leave empty to omit a date

@@

\lettrine[nindent=0em,lines=3]{T} he manuscript by Lin, Shi and Xue outlines how a Generative Adversarial Network (GAN) was developed to generate adversarial malicious network data and successfully evade any black-box intrusion detection system (IDS). The manuscript aims to fill a void in research into attacks on IDS, and particularly the use of GANs in such attacks.

@@

Listed below are the milestones covered by the paper: 
\begin{itemize}

\item An overview of why IDSGAN is necessary to build robust intrusion detection systems, and highlights on the lack of work done in IDS evasion, specifically using GANs.

\item A brief explanation of why Wasserstein GAN was preferred over other variants or the vanilla GAN, and outlines how the GAN architecture had been used to train the generator to generate adversarial data.

\item Usage of a benchmark dataset, NSL-KDD, consisting of network data for both normal and malicious traffic, which had been divided to be separately fed into the black-box IDS and the GAN discriminator and generator.

\item Visual representations of the modified architecture of Wasserstein GAN used for training the generator. It also specifies the layers used in the generator to add noise to the malicious data from the dataset.

\item Detailed layout of the discriminator and generator, the role of a black-box IDS in helping to train the discriminator and eventually the generator to evade the black-box. Also provided are the training algorithms, pseudo code for the same, loss functions and formulae used.

\item Extensive supporting data and graphs to throw light on how current IDSs are vulnerable to adversarial attacks and how the GAN framework developed was successful in evading most models used as a black-box.

\end{itemize}

@@

\section{Best Elements}
Below mentioned are the best elements of the paper:
\begin{itemize}

\item The paper has been aimed to contribute to the field of intrusion detection and evasion, and has successfully presented that current IDSs are nowhere near being secure against adversarial attacks.

\item All conclusions, facts and experiments have been well-supported with relevant data and graphs. The graphs clearly highlight how the IDSGAN was successful in evading all the models used for the black-box.

\item Using the predicted output labels of the black-box as target labels for the discriminator in the Wasserstein GAN used was an innovative way to train the discriminator with parameters having values as close as possible to those of the black-box. This helped the generator to train and accordingly add noises to malicious examples that successfully evade the IDS.

\item All equations, formulae and algorithms mentioned have been lucidly presented such that even with basic knowledge, the paper can be understood and appreciated.

\end{itemize}
%------------------------------------------------
%
\section{Limitations}
The limitations of the paper are listed below:
\begin{itemize}

\item The paper has clearly not been proof-read adequately. It is filled with grammatical errors. Often the sentences are too garbled to make out the true meaning, and other times, some words have been morphed such that the actual meaning of the sentence changes.

\item There are also informational errors, occurring while describing the values in NSL-KDD, errors in images and pseudo-code, which could have been avoided. Also, some parts of the text has been left in ambiguity.

\item Since the dataset has less data under U2R and R2L categories of attacks, the paper's claim that the GAN has successfully evaded IDS with those attacks is trivial and weak.

\end{itemize}
%
%-----------------------------------------------------------------------
%
\section{Opinion}
~~~~~While the idea and solution presented here is novel and standard procedures for experiments and data representation have been used, the paper itself is of average quality filled with mistakes and errors, easily avoidable had it been proof-read properly.
%
%-----------------------------------------------------------------------
